Indexing Variation Graphs\footnote{This work was supported by the Wellcome Trust grant [098051].}

### 2016-04-21 paper/paper.tex
Updated submission.

Now let $P'' = v''_{0} \dotsm v''_{\abs{X}-1}$ be a path matching pattern $X$ in graph $G''$. If $\abs{X} = 1$, we can choose any $v_{0} \in V_{d}(v''_{0})$. Now assume that we have chosen node $v_{j+1}$ from the equivalence class $V_{d}(v''_{j+1})$ and that $X[j+1, \abs{X}-1]$ is a prefix of $G_{d}.\gkey(v_{j+1})$. As edge $(v''_{j}, v''_{j+1}) \in E''$ exists, it must be that $\abs{G.\gpred(v, X[j])} > 0$ for a node $v \in G''.\gvalue(v''_{j+1}) = G_{d}.\gvalue(v_{j+1})$. Therefore substring $X[j] \cdot G_{d}.\gkey(v_{j+1})$ exists in $\mathcal{S}$, and the node $v_{j} \in V_{d}$ with $G_{d}.\gkey(v_{j}) = (X[j] \cdot G_{d}.\gkey(v_{j+1}))[0, k-1]$ has $X[j, \abs{X}-1]$ as a prefix of its key. As $G''.\gkey(v''_{j})$ is a prefix of $X[j] \cdot G_{d}.\gkey(v_{j+1})$, it is also a prefix of $G_{d}.\gkey(v_{j})$, and hence $v_{j} \in V_{d}(v''_{j})$. When $j = 0$, we can extend the substring as above to get a path matching the pattern in $G_{d}$, with $v_{0}$ as the start node.

>>>>

Now let $P'' = v''_{0} \dotsm v''_{\abs{X}-1}$ be a path matching pattern $X$ in graph $G''$. If $\abs{X} = 1$, we can choose any $v_{0} \in V_{d}(v''_{0})$. Now assume that we have chosen node $v_{j+1}$ from the equivalence class $V_{d}(v''_{j+1})$ and that $X[j+1, \abs{X}-1]$ is a prefix of $G_{d}.\gkey(v_{j+1})$. As edge $(v''_{j}, v''_{j+1}) \in E''$ exists, it must be that $\abs{G.\gpred(v, X[j])} > 0$ for a node $v \in G''.\gvalue(v''_{j+1})$. Therefore substring $X[j] \cdot G''.\gkey(v''_{j+1})$ exists in $\mathcal{S}$.

Let $Y$ be the longer of strings $G''.\gkey(v''_{j})$ and $X[j] \cdot G''.\gkey(v''_{j+1})$. As $Y$ is a substring of $\mathcal{S}$, there is a node $v_{j} \in V_{d}$ such that key $G_{d}.\gkey(v_{j})$ prefix-matches $Y$. Key $G_{d}.\gkey(v_{j})$ has both $X[j, \abs{X}-1]$ and $G''.\gkey(v''_{j})$ as its prefixes, and hence $v_{j} \in V_{d}(v''_{j})$. When $j = 0$, we can extend key $G_{d}.\gkey(v_{0})$ to get a path starting from $v_{0}$ and matching $X$ in graph $G_{d}$.
